Staged Abstract Interpreters

### 2019-08-15 paper/50_stageabs.tex
update

\paragraph{Are Monads Necessary?} No. One can always inline the monads and
obtain an abstract interpreter in continuation-passing style, or simply use
explicit side-effects such as mutation to implement the artifact with the same
abstract semantics. In either case, we can still apply the staging schema to
the abstract interpreter. As evidence, we provide a staged abstract
interpreter written in direct-style in the accompanying artifact.

>>>>

\paragraph{Monadic-style vs Direct-style} We use monadic interpreter through the paper,
but it is not necessary for staging. One can inline the monadic
operations and obtain an abstract interpreter in continuation-passing
style, or even translate back to direct-style that may use explicit
side-effects such as mutations. In either case, we can still apply the
staging idea to the abstract interpreter and remove the interpretation
overhead. Although, monads make the staged abstract interpreter can be
implemented in a modular and extensible way.
